Accurate binding of sodium and calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-12-11 Manuscript/manuscript.tex
Manuscript TODO cleanup

\begin{figure}[tb!]
  \centering
  \includegraphics[width=8.2cm]{../Fig/ipython_nb/Order-parameters_form-factors_exp-L14-ECCL17_q80_sig89.pdf}
  \includegraphics[width=7.4cm]{../Fig/POPCstructure.eps}
  %\includegraphics[width=8.0cm]{../Fig/ipython_nb/Order-parameters_exp-L14-ECCL17_q80_sig89.pdf}
  %\includegraphics[height=8.4cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \caption{\label{simVSexpNOions}
    Top: X-ray scattering form factors from simulations with the Lipid14 \cite{dickson14} and
    the ECC-POPC models compared with experiments~\cite{kucerka11} at 303~K.
    Middle: Order parameters of POPC head group, glycerol backbone and acyl chains 
    from simulations with the Lipid14 \cite{dickson14} and the ECC-POPC models
    compared with experiments \cite{ferreira13} at 300~K.
    The size of the markers for the head group order parameters correspond to
    the error estimate $\pm 0.02$ for experiments \cite{botan15,ollila16},
    while the error estimate for simulations is $\pm 0.005$.
    The size of the points for acyl chains are decreased by a factor of 3 to improve the clarity of the plot.
    Bottom: The chemical structure of POPC and the labeling of the carbon segments.
  } 
    \todo{Joe: I'm fine with the name change from ECC-lipids to ECC-POPC, but we have to be consistent throughout the text. I changed all accurences of ECC-lipids to ECC-POPC in the text, I yet need to change all figure legends then.}
\end{figure}

@@

\todo{Dynamics check is missing: MSD (Hector/Joe)}

@@

\begin{figure}[tb!]
  \centering
  \includegraphics[width=8.0cm]{../Fig/isocontours_r37_ca_O-carb.png} %\\
%  \includegraphics[width=8.0cm]{../Fig/volmap_resid10_Ca_Cl_PO4Cent.png} %\\
%  \includegraphics[width=4.0cm]{../Fig/volmap_resid10_Ca_Cl_sn1Cent.png}
%  \includegraphics[width=3.6cm]{../Fig/volmap_resid10_Ca_Cl_sn2Cent.png}
  \caption{\label{fig:volmaps}
      Isocontours of spatial number density of \ce{Ca^{2+}} (cyan, 0.0015~\AA$^{-3}$) 
      and POPC carbonyl oxygen atoms (red, 0.0075~\AA$^{-3}$). 
      Calcium cations localize mostly around phosphate oxygens.
      Interactions with carbonyl oxygens is less likely than with phosphate oxygens, 
      and it is contributed more by other neighbouring phospholipids than by the same lipid. 
      Transparent structures are shown to depict the variability of POPC configurations. 
      The number density was evaluated for each lipid, 
      after its strucutral alignment using only phosphate group. 
      %moiety, side chain 1 carbonyl group and side chain 2 carbonyl group.
      %Shown contours suggest that the dominant contribution 
      %to \ce{Ca^{2+}} binding comes from the phosphate oxygens,
      %whereas the interactions with any of the two carbonyl groups are considerably milder.
  }
  \todo{The figure should be updated as discussed last week. Joe: Will only smoothen the isosurfaces now. }
\end{figure}

>>>>

\begin{figure}[tb!]
  \centering
  \includegraphics[width=8.2cm]{../Fig/ipython_nb/Order-parameters_form-factors_exp-L14-ECCL17_q80_sig89.pdf}
  \includegraphics[width=7.4cm]{../Fig/POPCstructure.eps}
  %\includegraphics[width=8.0cm]{../Fig/ipython_nb/Order-parameters_exp-L14-ECCL17_q80_sig89.pdf}
  %\includegraphics[height=8.4cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \caption{\label{simVSexpNOions}
    Top: X-ray scattering form factors from simulations with the Lipid14 \cite{dickson14} and
    the ECC-POPC models compared with experiments~\cite{kucerka11} at 303~K.
    Middle: Order parameters of POPC head group, glycerol backbone and acyl chains 
    from simulations with the Lipid14 \cite{dickson14} and the ECC-POPC models
    compared with experiments \cite{ferreira13} at 300~K.
    The size of the markers for the head group order parameters correspond to
    the error estimate $\pm 0.02$ for experiments \cite{botan15,ollila16},
    while the error estimate for simulations is $\pm 0.005$.
    The size of the points for acyl chains are decreased by a factor of 3 to improve the clarity of the plot.
    Bottom: The chemical structure of POPC and the labeling of the carbon segments.
  } 
\end{figure}

@@

%\todo{Dynamics check is missing: MSD (Hector/Joe)}

@@

\begin{figure}[tb!]
  \centering
  \includegraphics[width=8.0cm]{../Fig/isocontours_r37_ca_O-carb.png} %\\
%  \includegraphics[width=8.0cm]{../Fig/volmap_resid10_Ca_Cl_PO4Cent.png} %\\
%  \includegraphics[width=4.0cm]{../Fig/volmap_resid10_Ca_Cl_sn1Cent.png}
%  \includegraphics[width=3.6cm]{../Fig/volmap_resid10_Ca_Cl_sn2Cent.png}
  \caption{\label{fig:volmaps}
      Isocontours of spatial number density of \ce{Ca^{2+}} (cyan, 0.0015~\AA$^{-3}$) 
      and POPC carbonyl oxygen atoms (red, 0.0075~\AA$^{-3}$). 
      Calcium cations localize mostly around phosphate oxygens.
      Interactions with carbonyl oxygens is less likely than with phosphate oxygens, 
      and it is contributed more by other neighbouring phospholipids than by the same lipid. 
      Transparent structures are shown to depict the variability of POPC configurations. 
      The number density was evaluated for each lipid, 
      after its strucutral alignment using only phosphate group. 
      %moiety, side chain 1 carbonyl group and side chain 2 carbonyl group.
      %Shown contours suggest that the dominant contribution 
      %to \ce{Ca^{2+}} binding comes from the phosphate oxygens,
      %whereas the interactions with any of the two carbonyl groups are considerably milder.
  }
  %\todo{The figure should be updated as discussed last week. Joe: Will only smoothen the isosurfaces now. }
\end{figure}
